---
title: "UK REF Impact Case Studies"
author: "Perry Stephenson"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{refimpact}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r message=FALSE}
library(refimpact)
```

# Worked Example

# Detailed Walkthrough

The core function for this package is `ref_get()`, which takes an API method as
the first argument, and some optional arguments depending on the method.

The API methods available are detailed below. 

## SearchCaseStudies

This is the core method of the API, and the most important for users of this
package. The search method requires a compulsory argument to the `ref_get()`
function: `query`. This arguments takes a list of query parameters, which can be
as simple as a single Case Study ID, which returns a single record. A query
returning a single record is shown below to demonstrate the syntax and the 
returned data structure; more complex queries will be shown later in the 
vignette.

```{r}
results <- ref_get("SearchCaseStudies", query=list(ID=941))
print(results)
```

You will note that the function returns a nested tibble - that is a tibble with
other data frames inside it. This means that you can interrogate the tibble as
per usual:

```{r}
cat(results[[1, "CaseStudyId"]])
cat(results[[1, "Title"]])
cat(strtrim(results[[1, "ImpactSummary"]], width = 200), "<truncated>")
cat(strtrim(results[[1, "ImpactDetails"]], width = 200), "<truncated>")
cat(results[[1, "Institution"]])
```

You can also interrogate the nested fields the same way, and even subset them:

```{r}
print(results[[1, "Country"]])
print(results[[1, "Institutions"]])
print(results[[1, "Institutions"]][,c("UKPRN", "InstitutionName")])
```

> _In the opinion of the package author, the nested tibble offers many advantages 
over other data representations - it is a relatively straight-forward exercise
to transform the data into a set of wide or narrow tables if required._

Returning a single case study based on the ID is obviously a niche use-case, so
there are some other ways to search the database. But before getting to those, 
it is worth pointing out that you can select multiple case studies in a single
query:

```{r}
results <- ref_get("SearchCaseStudies", query=list(ID=c(941, 942, 1014)))
print(results)
```

The ID parameter above is an exclusive parameter - if you provide one or more 
IDs then the function will print a warning to the console, and remove all 
parameters except for the IDs. This is based on the API's documented 
limitations.

The other parameters can all be combined for searching. Those parameters are:

* **UKPRN** - This is a code referencing an institution, and comes from the 
  ListInstitutions method below. Takes a single UKPRN.
* **UoA** - This is a code referencing a Unit of Assessment, and comes from the
  ListUnitsOfAssessment method below. Takes a single ID.
* **tags** - This is one or more codes referencing tags from the ListTagValues 
  method. The tags are separated into 13 different TagTypes, which are detailed
  below. When multiple tags are provided to the search method, it will only 
  return rows which contain both tags.
* **phrase** - You can search the database using a text query. The query must
  conform to Lucene search query syntax.
  
Some examples are shown below.

```{r}
results <- ref_get("SearchCaseStudies", query=list(UKPRN = 10007777))
dim(results)
results <- ref_get("SearchCaseStudies", query=list(UoA = 5))
dim(results)
results <- ref_get("SearchCaseStudies", query=list(tags = c(11280, 5085)))
dim(results)
results <- ref_get("SearchCaseStudies", query=list(phrase = "hello"))
dim(results)
results <- ref_get("SearchCaseStudies", query=list(UKPRN = 10007146,
                                                   UoA   = 3))
dim(results)
```

Unfortunately, the API method requires at least one search parameter, which 
makes it more difficult to download the entire dataset. A short script for this
purpose is included at the end of this vignette.

## ListInstitutions

This method lists all of the institutions which are included in the REF Impact
Case Studies database, and the UKPRN column in the resuling tibble can be used
as a query parameter

```{r}
institutions <- ref_get("ListInstitutions")
print(institutions)
```

## ListTagTypes and ListTagValues

These methods provide tags which can be used as search parameters in the 
SearchCaseStudies method. The ListTagTypes method returns the types of tags 
available:

```{r}
tag_types <- ref_get("ListTagTypes")
print(tag_types)
```

These tag types can then be used as an argument to the ListTagValues method, to
get all tags for each type:

```{r}
tag_values_5 <- ref_get("ListTagValues", 5)
print(tag_values_5)
```

This can take some time to iterate through, so the full table is bundled with 
this package. You can access it via `ref_tags`:

```{r}
print(ref_tags)
```

